Deep Learning for 3D Brain Activity Scans

### 2019-11-30 paper/submission.tex
Ready to start graphing/writing up paper, 3d successful but not ostensibly more than 2d

>>>>

% ----------------------------------------------------------------------
% TODO
% ----------------------------------------------------------------------
\section{TODO}\label{sec:todo}

NN project
- 2d hyperparameters, let's use a LR scheduler? LR spikes all over the place still, why?

- 3d CNN - typically meant for video classification using time as the third axis,
here we are not using time, though that is a dimension we have access to,
though doesn't make sense for this experiment/project to try to add in
- https://pytorch.org/docs/stable/torchvision/models.html#video-classification

- scheduler / hyperparams / diff architectures (just go with res3d, res2d+1d, mix three types
- cut batch size to avoid scaling down images (TRIED NO BUENO?)

be sure to talk about everything in paper

normalization/mean image
interpolation
wrestling with memory constraints (batch size / 3d data huge for cpu/gpu, dataset pretty large in general for ram) slow learning, tapering off learning
different styles of 1d (unfurl 3d, 2d) 2d (mean flattened, one slice) 3d (scale, orig)
LR explorations
sanity checks on brain image data, impossible for me to spot the differences

batch_size and interpolation hard to juggle too?
3d feels like "luck" plays a big part of getting training to catch/start
seems like scaling down is pretty important and I have better luck with larger batch sizes (meaning scale down is crucial) wonder if aggressive scale down is worthwhile, like over 3./4, image gets real grainy real fast)

images:
LR / accuracy measures, of diff approaches
hi res, mid res, interpolated down res brain scan examples,
2d slice example
total training time? num features comparison
average slice image
graphs from 2d training, 3d takes legit 2-3 hours for 200 epochs on 6 subjects with 5./6 & 7. / 2.

inclusion of more ppts/subjects means more training time (val/test are of same patients,
hence more individual brain shapes means more general, but longer to learn)
20 epochs to see liftoff of 55% with 10 ppts, vs quicker with 6ppts

image segmentation attempt?
saliency maps?
filter views?

torch save models - can eval that way
host for downloads?

future works
better gpu / computer might be important, the 3d models are real fucking beasts to train, and their data is large as fuck
model ensemble (free extra few percent perf)

findings: 3d is cool, but crazy prohibitively slow and not much better than 2d without more refinements. IMHO theres
promise still in exploring it, but given the inexcusable runtime and datasize 2d is probably worth more investment
unless better hardware or serious effort is expended in getting it differentiable
